Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-11 R0V0.tex
Finish first round of proof of clique decomposition
Erase the result regarding diagonal dominance

Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=&\ \{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		&\ \arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},\\
		&\ k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}_k$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.

@@

\end{proof}

Consider the smooth function $T:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times n}$ with elements $i,j\in\mathbb{N}_{[1,N]}$ defined as
	\begin{subequations}\label{eq:T}
	\begin{align}
		T_{ii}=-\dot{W}_i+A_{ii}W_i+W_iA_i^\top+B_iY_{ii}+(B_iY_{ii})^\top\nonumber\\
		+2\lambda_i W_i
	\end{align}
	and
	\begin{equation}
		T_{ij}=A_{ij}W_j+W_iA_{ji}+B_iY_{ij}+(B_jY_{ji})^\top.
	\end{equation}
	\end{subequations}

\begin{definition}\label{def:}
	The matrix $T$ is said to be \emph{block-diagonally dominant} if the inequality
	\begin{equation}\label{eq:BDD}
		|T_{ii}^{-1}|^{-1}\geq\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|,
	\end{equation}
	holds, for every index $i\in\mathbb{N}_{[1,N]}$ and for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$.
\end{definition}

\begin{corollary}\label{cor:distributed computation}
	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
	\begin{equation}\label{eq:MI formulation:i}
		T_{ii}\prec 0
	\end{equation}
	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation}.
\end{corollary}

\begin{proof}[Proof of Corollary~\ref{cor:distributed computation}]
	By assumption, the pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation:i} and the matrix $T$ with components defined by the set of equations \eqref{eq:T} is block-diagonally dominant.

	Equation \eqref{eq:BDD} together with the fact that $|I_{n_i}|\leq |T_{ii}||T_{ii}^{-1}|$ implies that the inequality
	\begin{equation}\label{eq:BDD2} 
		\sum_{\substack{j=1\\ j\neq i}}^N|T_{ij}|\leq |T_{ii}|
	\end{equation}
	holds, for every index $i\in\mathbb{N}_{[1,N]}$.

	For every $\delta_\eta\in\mathbb{R}^n$, consider the product $\delta_\eta^\top T\delta_\eta$. Each line $i\in\mathbb{N}_{[1,N]}$ of this product is given by
	\begin{equation*}
		\delta_{\eta_i}^\top\begin{bmatrix}
			T_{i1}&\cdots&T_{i(i-1)}&T_{ii}&T_{i(i+1)}&\cdots&T_{iN}
		\end{bmatrix}\delta_\eta.
	\end{equation*}
	Inequalities \eqref{eq:BDD2} and \eqref{eq:MI formulation:i} imply that the inequalities
	\begin{equation*}
		\sum_{\substack{j=1\\ j\neq i}}^N\delta_{\eta_i}^\top T_{ij}\delta_{x_j}\leq \delta_{\eta_i}^\top T_{ii}\delta_{\eta_i}< 0
	\end{equation*}
	hold, for every $\delta_\eta\in\mathbb{R}^n$. Consequently, the inequality $\delta_\eta^\top T\delta_\eta\leq 0$ holds, for every $\delta_\eta\in\mathbb{R}^n$. This later inequality is equivalent to the MI \eqref{eq:MI formulation}. This concludes the proof of Corollary~\ref{cor:distributed computation}.
\end{proof}

>>>>

Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		\arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}_k$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.

@@

   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$. The existence of $p$ cliques implies that there exist matrices $F_1,\ldots,F_p$ such that the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k
  	\end{equation*}
  	holds.

  	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
  	\begin{equation*}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
	\end{equation*}
	This concludes the proof.
\end{proof}
